A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Cropped the map and added a caption

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap-color}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{A map of the number of workers per country.  This is map is generated based on ((the self-reported location / geolocation of IP address)) of the XXXX workers in our study.  The size of the circles represents the number of worker from each country.  The largest are India (1082 workers), the United States (XXX), XXX (XXX) and XXX (XXX).  To calibrate the sizes: the Philippines has XXX workers, Egypt has XXX, and Russia has XXX.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
